Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-18 2015-turklang-kazdep/paper.tex
spacing more like what they're asking for
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60812 72bbbca6-d526-0410-a7d9-f06f51895060
floss
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60815 72bbbca6-d526-0410-a7d9-f06f51895060
some sources
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60818 72bbbca6-d526-0410-a7d9-f06f51895060
updates
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60824 72bbbca6-d526-0410-a7d9-f06f51895060
desc. corp
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60825 72

\documentclass[a4paper,11pt,twocolumn]{article}

@@

\title{Towards a universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA\footnote{Corresponding author.  E-mail address: jonwashi@indiana.edu}}

@@

\abstract{hargle treebank bargle dependency grammar}

@@

\citet{hargle}

@@

>>>>

\documentclass[a4paper,11pt, onecolumn]{article}

@@

\title{Towards a free/open-source universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA\footnote{Corresponding author.  E-mail address: jonwashi@indiana.edu}}

@@

\abstract{250-300-word ``extended abstract in English''}

@@

\citet{Lynn12}, \citet{Atalay03}, \citet{Oflazer03}, \citet{DeMarneffe14}

@@

\subsection{Corpus}

\begin{table}
  \centering
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    UDHR & Legal text on human rights & - & - & - \\
    Phrasebook & Phrases from Wikitravel & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз & Philosophical text & 34 & 525 & 15.4 \\ 
    Өлген қазан & Folk tale & 8 & 140 & 17.5 \\
    Азамат къайда? & Story for children and language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014  & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran) & - & - & - \\
    Радиан & Wikipedia article (Radian) & - & - & - \\
    \hline
  \end{tabular}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types.}
\end{table}

\subsection{Preprocessing}

% tokenisation
\cite{Washington14}

\subsection{Annotation guidelines}

\begin{table}
  \centering
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Label} & \textbf{Description} \\

    \hline
  \end{tabular}
  \caption{Universal dependency label set}
\end{table}

\section{Evaluation}

\section{Future work}

%crosslingual parsing: Tatar, Kumyk, Kyrgyz, Tuvan
